\speculake: Hiding Malware in Speculative Execution

### 2018-08-02 paper/architecture.tex
arch +sentence

We note a performance tradeoff between the size of communication (e.g. 4 bits vs 8
bits) and the time it takes the real world to recover the result from the side
channel. Using Flush+Reload~\cite{yarom2014flush+} as our cache side channel,
recovering the result requires accessing all elements in an array exponential in
the size of the result (e.g. $2^8$ array reads to recover an 8-bit result).
Therefore, there is a
performance advantage for keeping the size of the result small, and communicating
out small pieces of information that are aggregated by the real world.
Meanwhile, smaller channels introduce more overhead in recovering information. We
investigate this tradeoff in Section~\ref{subsec:impl-aes}, and find that 8~bits
is near optimal.

>>>>

We note a performance tradeoff between the size of communication (e.g. 4 bits vs 8
bits) and the time it takes the real world to recover the result from the side
channel. Using Flush+Reload~\cite{yarom2014flush+} as our cache side channel,
recovering the result requires accessing all elements in an array exponential in
the size of the result (e.g. $2^8$ array reads to recover an 8-bit result).
Therefore, there is a
performance advantage for keeping the size of the result small, and communicating
out small pieces of information that are aggregated by the real world over multiple speculative executions.
Meanwhile, smaller channels introduce more overhead in recovering information. We
investigate this tradeoff in Section~\ref{subsec:impl-aes}, and find that 8~bits
is near optimal in practice.
